article title

### 2024-12-13 article.tex
Edit cotnent

@@

@@

@@

For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, \gls{anome}, \gls{iam}, \gls{pam}, \gls{edr}, \glsxtrlong{xdr}, \gls{pythonnamespace}, \gls{cybersecurity}.

@@

\newpage
\printunsrtglossary[type={abbreviations}]

>>>>

% use this package for better control over quotes
\usepackage{csquotes}

@@

\usepackage{xcolor}

@@

% the above shows every single term in pilon_gilles_glossary.bib
% use the following instead when only list terms used in the document

% \GlsXtrLoadResources[
%     src={~/documents/repositories/latex/pilon_gilles_glossary.bib},
%     selection={recorded and deps},
%     sort=letter-nocase
% ]

@@

For glossary terms use \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, \gls{anome}, \gls{iam}, \gls{pam}, \gls{edr}, \glsxtrlong{xdr}, \gls{pythonnamespace}, \gls{cybersecurity}.

@@

% \newpage
% \printunsrtglossary[type={abbreviations}]
